%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans, 10pt]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\usepackage[latin1]{inputenc}


% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
% \usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Alexandre}{Imperiale}
\title{Research Engineer, Modeling \& Numerical Simulation}                               % optional, remove / comment the line if not wanted
\address{7 villa du bel air}{75012 Paris}{France}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[tel.]{+33~6~60~08~85~90}                   % optional, remove / comment the line if not wanted
\email{alexandre.imperiale@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{github.com/AlexandreImperiale}                         % optional, remove / comment the line if not wanted
\extrainfo{\href{https://twitter.com/asimperial?lang=fr}{@asimperial}}                 % optional, remove / comment the line if not wanted
% \photo[150pt][0.pt]{photo}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
% \quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Work experiences}

\cventry{Since 2013}{Research Engineer}{French Atomic Energy Commission (CEA)}{Saclay}{}{
	Development of a C++ computational kernel ($\approx$ 50 kLoC) combining a \textbf{high-order finite element method} with a \textbf{domain decomposition approach} for ultrasonic wave propagation modeling. \newline{}%
	\newline{}
	Major contributions:
	\newline{} \vspace{-8pt}
		\begin{itemize}
		\item Development of a specific model of the computational platform \href{http://www.extende.com/fr}{CIVA} ($\approx$ 1 MLoC) for the \textbf{modeling and numerical simulation of guided wave propagation in stratified composite plates},
		\newline{} \vspace{-8pt}
		\item Implementation, embedded within the \href{http://www.extende.com/fr}{CIVA} platform, of coupling procedures between the finite element kernel and a ray-based asymptotic model. Application to the \textbf{modeling of ultrasonic waves and their interactions with complex flaws.}
		\end{itemize}
	\vspace{8pt}	
	Co-supervision of doctoral degree:
	\vspace{8pt}	
		\begin{itemize}
		\item 2014--2017, \textit{A hybrid method coupling the integral equation method with the ray tracing method - Application to non-destructive testing,} in collaboration with l'UMA - ENSTA ParisTech,
		\newline{} \vspace{-8pt}
		\item 2015--2018, \textit{Multi-level parallelization of a finite element code based upon a domain decomposition strategy - Application to non-destructive testing} in collaboration with LIP6, UPMC.
		\end{itemize}
	\vspace{8pt}	
}

\cventry{2010--2013}{Ph.D. in applied mathematics}{INRIA}{Saclay}{}{
Ph.D. in applied mathematics at the French Institute for Research in Computer Science and Automation. The manuscript entitled:  
\textit{Image-based data assimilation methods for the personalisation of mechanical models - Application to cardiac mechanics and tagged-MRI}, is available \href{https://tel.archives-ouvertes.fr/tel-00936027}{online} (in English).}

\section{Educational background}
\cventry{2010--2013}{Ph.D. degree}{INRIA Paris-Saclay \& Université Pierre et Marie Curie}{}{}{Ph.D. in applied mathematics.}  % arguments 3 to 6 can be left empty
\cventry{2009--2010}{Master degree}{Université de Rouen}{}{}{Master degree in fundamental and applied mathematics.}
\cventry{2005-2010}{Engineering degree}{INSA Rouen}{}{}{Engineering degree at the French Institut of Applied Sciences, dpt. of mathematics, in Rouen.}

\section{Development skills}
\cvitem{\small{\textit{Main language}}}{C++11/14/17, metaprogramming, computational kernel interfacing, parallelism \& multithreading, notions of GPU development,}
	\vspace{8pt}	
\cvitem{\small{\textit{Other languages}}}{Rust, Python, Matlab, notions of front-end web development (html, css, js),}
	\vspace{8pt}	
\cvitem{\small{\textit{Env.}}}{Microsoft Visual Studio (MSVC compiler), MacOS XCode (gcc/clang compiler), git versionning (SmartGit, GitHub),}
	\vspace{8pt}	
\cvitem{\small{\textit{Personal open-source projects}}}
{
	\vspace{-6pt}	
	\begin{itemize}
		\item \href{https://github.com/AlexandreImperiale/mersh}{mersh}, a module written in Rust programming language for the manipulation of meshes and their associated geometric tools,
			\vspace{3pt}
		\item \href{https://github.com/AlexandreImperiale/grillomatic}{grillomatic}, a light C++ kernel for the resolution of elastodynamic equations in 2D for any kind of constitutive law,
					\vspace{3pt}
		\item \href{https://github.com/AlexandreImperiale/wave1D}{wave1D}, a Python model for modeling 1D wave propagation using a multi-scale method.
		\end{itemize}
}

\section{Languages}
\cvitemwithcomment{French}{Mother tongue}{}
\cvitemwithcomment{English}{Fluent}{Everyday use in scientific communications}
\cvitemwithcomment{Greek}{Advanced level}{Courses of the IENHP}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{habbrvyr}
{\footnotesize
\bibliography{../publications}}
% \bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template.tex'.
